---
title: "Twitter roundup June 2020"
categories:
  - Twitter posts
description: |
  Microsocpy based twitter posts that have caught my attention this month
draft: false
author:
  - name: Mark Rigby 
    affiliation: Nikon Insturments UK
    position: Advanced Imaging Specialist
    affiliation_url: https://www.microscope.healthcare.nikon.com/
preview: images/twitter_logo.PNG
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
library(twitterwidget)
library(knitr)

```



## Connected papers


```{r twitter 0, layout="l-body"}

twitterwidget('1268282414402613249')

```



##  Nikon webinar July 15th 

Operating an Imaging Core Facility During a Pandemic

```{r twitter 1, layout="l-body"}

twitterwidget('1275476089960304643')

```
<br>
<br>
<br>
<br>
<br>
<br>
<br>

##  Super-resolution optical fluctuation imaging

SOFI application note from Photometrics

```{r twitter 2, layout="l-body"}

twitterwidget('1275783624969932800')

```
<br>
<br>
<br>
<br>
<br>


##  Super resolution cheat sheet

Link to J Cell Science poster by Henriques and Leterrier labs 'Cell biologists guide to super resolution microscopy'

```{r twitter 3, layout="l-body"}

twitterwidget('1275178839333842951')

```


##  Lego microscope

```{r twitter 4, layout="l-body"}

twitterwidget('1267374722280554498')

```
<br>
<br>
<br>





##  Refractive index


```{r twitter 5, layout="l-body"}

twitterwidget('1267617289987174401')

```
<br>
<br>
<br>





##  Nikon N-SIM-S imaging of endoplasmic reticulum


```{r twitter 6, layout="l-body"}

twitterwidget('1277660055295471618')

```

<br>
<br>
<br>
<br>
<br>
<br>


